\begin{rubric}{Outreach, Public Engagement \& Volunteering }

\subrubric{Longer Term Initiatives}
\entry*[2023 -- 2024]%$\cdots\cdot$]%
    \textbf{President}, International Workshop for Astronomy e.V. (IWA), Germany.
\entry*[2017 -- 2024]%-- $\cdots\cdot$ ]%
    \textbf{Leader}, International Astronomical Youth Camp (IAYC), Germany. 
\entry*[2021 -- 2023]%
    \textbf{Vice President}, International Workshop for Astronomy e.V. (IWA), Germany. 
\entry*[2019 -- 2022]%
    \textbf{Outreach volunteer}, Keele Observatory and with the Keele University Stardome.
\entry*[2019 -- 2020]%
    \textbf{Organiser}, Pint of Science Stoke-on-Trent, UK.
\entry*[2016 -- 2018]%
    \textbf{Founder and President}, University of Warwick Astronomy Society, Coventry, UK.
\entry*[2017 -- 2018]%
    \textbf{Outreach volunteer}, University of Warwick Department of Physics, UK. 
\entry*[2016 -- 2018]%
    \textbf{STEM Ambassador}, STEMNET, West Midlands, UK.

\subrubric{Standalone Events}
\entry*[2022]%
    \textbf{Ardingly College International Women's Day event}, online -- \textit{panel}
\entry*[2021]%
    \textbf{eIAYC Seminar Series}, online -- \textit{talk}
\entry*[2021]%
    \textbf{Ardingly College Physics Careers event}, online -- \textit{talk}
\entry*[2021]%
    \textbf{Astro Radio}, online -- \textit{interview}
\entry*[2020]%
    \textbf{Wirral \& Merseyside Women's Engineering Society}, online -- \textit{talk}  
\entry*[2020]%
    \textbf{Global Science Show LGBT+ STEM day event}, online -- \textit{short-form}  
\entry*[2019]%
    \textbf{Pint of Science}, Stoke-on-Trent, UK -- \textit{talk} 
\entry*[2019]%
    \textbf{Keele University International Day of Women and Girls in Science event}, Keele, UK -- \textit{panel} 
\entry*[2019]%
    \textbf{University of Warwick Astronomy Society}, Coventry, UK -- \textit{talk} 
\entry*[2018]%
    \textbf{ESO Astronomy Camp}, St Barthelemy, Italy -- \textit{event}
\entry*[2018]%
    \textbf{Stoking Curiosity}, Stoke-on-Trent, UK -- \textit{talk}
\entry*[2018]%
    \textbf{Kings High School}, Warwick, UK -- \textit{talk} 
\entry*[2017]%
    \textbf{ESO Astronomy Camp}, St Barthelemy, Italy -- \textit{event}
    
\end{rubric}